Boccaccio example: end to end truth for California Current

### 2019-05-27 FullBoccaccioTruthEx.Rmd
Z correction broken here too but pattern more apparent for further diagnosis

```{r testagecl, eval=FALSE}
# add YOY file to the config files
YOY <- load_yoy(d.name, paste0("output", scenario.name, "YOY.txt"))

@@

trueagesall <- calc_stage2age(nums_data = truth$nums,
                                 biolprm = biol, 
                                 yoy = YOY,
                                 fgs = funct.groups, 
                                 runprm = runpar)

@@

```{r plotannage}

@@

# run survey  and sample fish on this for completeness?

# plot it

>>>>

```{r testagecl, eval = FALSE}
# add YOY file to the config files
YOY <- load_yoy(d.name, paste0("output", scenario.name, "YOY.txt"))

@@

trueagesall <- calc_stage2age(nums_data = survey_testNall,
                                 biolprm = biol, 
                                 yoy = YOY,
                                 fgs = funct.groups, 
                                 runprm = runpar)

@@

After corrections were applied to `calc_Z` we were closer to the ballpark in NOBA. This demonstrates that the estimated true ages are not working between the cohort ages, they just drop to 0. This is consistent with what we observed for NOBA. The numbers at true age [don't match atlantis output where we have it for NOBA](https://sgaichas.github.io/poseidon-dev/TestCalcZ.html), so I will do further testing with this function and `calc_stage2age`.

```{r plotannage, message=FALSE, warning=FALSE}

@@

# test with one species--this is still full polygon and layer output
trueNatage_ss <- trueNatage[trueNatage$species == "Bocaccio_rockfish",]

# run sample fish on this for completeness? yes to aggregate
trueNagesamp_ss <- sample_fish(trueNatage_ss, effNhigh)

# plot it--first few timesteps for bocaccio

Natageplot <- ggplot(trueNagesamp_ss, aes(x=agecl, y=atoutput)) +
  geom_point() +
  theme_tufte() +
  labs(subtitle = paste(scenario.name,
                        trueNatage_ss$species))
